\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-01-18 eg6-letters/NIM/review-1/review-1.tex
Update more on NIM review

\item I understand the resolution and efficiency have been evaluated with the 2 
   GeV electrons. Is it foreseen to analyze also the 6 GeV electron runs, which 
   were the actual data taking? Is there an evaluation of the foreseen RTPC 
   performances in that case?\\
\textcolor{blue}{It is not possible to do such studies with the 6 GeV beam, because 
of the lack of an exclusive process to use as elastic cross sections drops dramatically 
in our acceptance at such high energy. We would have loved to and tried many alternate
channels, but none was detectable with reasonnable statistics.}

>>>>

\item I understand the resolution and efficiency have been evaluated with the 2 
   GeV electrons. Is it foreseen to analyze also the 6 GeV electron runs, which 
   were the actual data taking? Is there an evaluation of the foreseen RTPC 
   performances in that case?\\
\textcolor{blue}{It is not possible to do such studies with the 6 GeV beam, because 
of the lack of an exclusive process to use. Elastic cross sections drops dramatically 
in our acceptance at higher energy and we could not find any suitable replacement. We 
have tried many alternate channels, but none was detectable with reasonnable statistics
in the 6~GeV data.}
